---
title: "Input"
output:
  pdf_document: 
    fig_caption: yes
    highlight: tango
  html_document:
    df_print: paged
vignette: >
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Input data

## Data format

The data format of input should be numerical only in the form of data frame, for example:

```{r, include = TRUE}
MaxWiK::Data.2D$X[1:4, ]
str(MaxWiK::Data.2D$X)
```

If you need use a matrix, please, transform it into the data frame first. If some columns have non-numerical type, please, transform them into numerical type using factors.

## Specificity of the data

The method is mostly appropriate for specific data which has sparse regions of interest. The package dataset `Data.2D` has an example where the lack of data points at the region of the interest (blue cross):

```{r, include = TRUE, fig.height=4, fig.width=4}
library('ggplot2')
df = MaxWiK::Data.2D$X; th = MaxWiK::Data.2D$sampling$theme.ggplot
obs = MaxWiK::Data.2D$observation$x0
ggplot(data = df, mapping = aes( x = par.sim.X1, y = par.sim.X2) ) +
    geom_point(size = 0.3) + th + 
    annotate('point', x= obs[1], y = obs[2] , colour="blue", shape = 4, size = 4)

```

## Input for Approximate Bayesian Computation and metasampling algorithm

Input for Approximate Bayesian Computation and metasampling algorithm are same. It includes parameters dataset, dataset of statistics of simulations, statistics of observation, and hyperparameters like $t$ and $\psi$.

## Input for sampling algorithm
