---
title: "Sampling"
output:
  pdf_document: 
    fig_caption: yes
    highlight: tango
  html_document:
    df_print: paged
vignette: >
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# MaxWiK sampling

If a generating model function is known then the MaxWiK sampling algorithm can be run. The input is the same as for metasampling with additional arguments for generating function:

-   model - the function of simulation;

-   arg0 - list of constant arguments for the model function.

To run algorithm properly, a user has to check the simulation first like:

```{r, include = TRUE, echo=TRUE, eval=FALSE}
do.call( what = model, args = c( arg0, list( x = c(5, 7) ) ) )
```

where $x$ is the variable of the model function. Using the same 2D example the sampling can be run as follow:

```{r, include = TRUE, echo=TRUE, eval=FALSE}
example.2D  = MaxWiK::Data.2D
obs         = as.data.frame( t ( example.2D$observation$A ) )
res.MaxWik  =  MaxWiK::Data.2D$ABC$result.MaxWiK
meta.sampling  =  meta_sampling( psi = example.2D$ABC$hyperparameters$psi, 
                                 t   = example.2D$ABC$hyperparameters$t, 
                                 param    = example.2D$X, 
                                 stat.sim = example.2D$Y, 
                                 stat.obs =  obs, 
                                 talkative = TRUE, 
                                 check_pos_def = TRUE,
                                 n_bullets = 42, 
                                 n_best = 12, 
                                 halfwidth = 0.5, 
                                 epsilon = 0.001, 
                                 rate = 0.2, 
                                 max_iteration = 10, 
                                 save_web = TRUE, 
                                 use.iKernelABC = res.MaxWik )
```

Please, pay attention that argument 'use.iKernelABC' can be skipped, by default it is set up to NULL and is generated for metasampling algorithm.

To get all the unique points from the 'spiderweb' list of the output data, one can run:

```{r, include = TRUE, echo=TRUE, eval=FALSE}
        network  = unique.data.frame( do.call(rbind.data.frame, meta.sampling$spiderweb ) )
```

There are plots for posteriori distribution of $X1$ and $X2$:

```{r, echo=FALSE, include = TRUE, fig.height=3, fig.width=5}
library('ggplot2')
th = MaxWiK::Data.2D$sampling$theme.ggplot
meta.sampling  =  MaxWiK::Data.2D$metasampling$result
network  = unique.data.frame( do.call(rbind.data.frame, meta.sampling$spiderweb ) )
obs = MaxWiK::Data.2D$observation
w = which(MaxWiK::Data.2D$metasampling$result$iKernelABC$similarity > 0)
posteriori.MaxWiK = MaxWiK::Data.2D$X[ w, ]
MaxWiK::my.ggplot.density( title = ' Posteriori distribution of X1 parameter', 
                   datafr1 = posteriori.MaxWiK, 
                   datafr2 = network, 
                   var.df  = 'par.sim.X1', 
                   obs.true = obs$x0[ 1 ], 
                   best.sim = as.numeric( meta.sampling$par.best[ 1 ] )
)
```

```{r, echo=FALSE, include = TRUE, fig.height=3, fig.width=5}
library('ggplot2')
th = MaxWiK::Data.2D$sampling$theme.ggplot
meta.sampling  =  MaxWiK::Data.2D$metasampling$result
network  = unique.data.frame( do.call(rbind.data.frame, meta.sampling$spiderweb ) )
obs = MaxWiK::Data.2D$observation
w = which(MaxWiK::Data.2D$metasampling$result$iKernelABC$similarity > 0)
posteriori.MaxWiK = MaxWiK::Data.2D$X[ w, ]
MaxWiK::my.ggplot.density( title = ' Posteriori distribution of X2 parameter', 
                   datafr1 = posteriori.MaxWiK, 
                   datafr2 = network, 
                   var.df  = 'par.sim.X2', 
                   obs.true = obs$x0[ 2 ], 
                   best.sim = as.numeric( meta.sampling$par.best[ 2 ] )
)
```

The red line is a true value, dotted is the best simulation, the red area is metasampling generated points (generated network), and the green area is the points taken from isolation kernel algorithm with similarity more than 0.
